\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-05 cfhtlens.tex
cfhtlens.tex Added numbers from Shahab's recent runs

\citet{kitching/etal:2016} choose to only vary $\sigma_8$ in their analysis, fixing all other parameters to their Planck values. They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) of the data from \citet{kilbinger/etal:2013}.    We argue that this artificial reduction in the error by a factor of $\sim 2$, in comparison to a full six-parameter fit, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.

We repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} finding the lowest conditional value of $\sigma_8 = XXX \pm XXX$ for the XXX case and the highest conditional value of $\sigma_8 = XXX \pm XXX$ for the XXX case.  As expected from the comparison in Figure~\ref{fig:Cl_xi} the different combinations of assuming flat or spherical sky, or baseline of extended Limber make little difference to the cosmological parameter constraints, even in this `one-parameter' analysis.

Our Limber-case findings are therefore in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to the Extended Limber spherical case in Table~\ref{tab:Tl_nu}).

>>>>

\citet{kitching/etal:2016} choose to only vary $\sigma_8$ in their analysis, fixing all other parameters to their Planck values. They find a conditional value of $\sigma_8 = 0.789 \pm 0.015$ for their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) of the data from \citet{kilbinger/etal:2013}.    We argue that this artificial reduction in the error by a factor of $\sim 2$, in comparison to a full six-parameter fit, could easily mislead, making it appear that the impact of removing all approximations from the theoretical analysis is more significant for current surveys than it is in reality.  Nevertheless, we repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} finding the lowest conditional value of $\sigma_8 = 0.743 \pm 0.023$ for the `Standard' (KSt) case and the highest conditional value of $\sigma_8 = 0.744 \pm 0.023$ for the `Baseline Limber Flat` (LF) case.  As expected from the comparison in Figure~\ref{fig:Cl_xi} the different combinations of assuming flat or spherical sky, or baseline of extended Limber make little difference to the cosmological parameter constraints, even in this `one-parameter' analysis.

We find our Limber-case findings to be in disagreement with \citet{kitching/etal:2016} who find a shift of $\Delta \sigma_8 = 0.007$ between their `standard' analysis (row 1 in Table~\ref{tab:Tl_nu}) and their `Limber' analysis (which we believe corresponds to the Extended Limber spherical (ELS) case in Table~\ref{tab:Tl_nu}).
